I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-12-30 submission/paper.tex
Minor correction.

Figure \ref{fig:esbjerg} shows flooding maps corresponding to the entries in Table \ref{tab:stormsurge}. These maps can be used to further develop adaptation policies for Esbjerg.
\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=\linewidth]{Floodmaps_Harbour.png}
\caption{Flood extents and depths for the city of Esbjerg in year 2100 during storm surges with a 20 year return period (upper row) and a 100 year return period (lower row) with (a) no sea level rise and with sea level rise corresponding to RCP 85 (5th percentile (b), median (c) and 95th percentile (d). }
\label{fig:esbjerg}
\end{center}
\end{figure}

>>>>

Figure \ref{fig:esbjerg} shows flooding maps corresponding to the entries in Table \ref{tab:stormsurge}. These maps can be used to further develop adaptation policies for Esbjerg.
\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=\linewidth]{Floodmaps_Harbour.png}
\caption{Flood extents and depths for the city of Esbjerg in year 2100 during storm surges with a 20 year return period (upper row) and a 100 year return period (lower row) with (a) no sea level rise and with sea level rise corresponding to RCP 85 (5th percentile (b), median (c) and 95th percentile (d)). }
\label{fig:esbjerg}
\end{center}
\end{figure}
